\chapter*{Acknowledgements}

\addcontentsline{toc}{chapter}{Acknowledgements}

Throughout the writing of this dissertation (and my whole university career) I have received a great deal of support and assistance.

I would first like to thank my external supervisor, Professor Pierre Senellart, whose expertise and constant support have been fundamental in sharpening my thinking and bringing my work to a higher level. In addition to his great professionalism and precision, the humanity that characterizes him has been of great help in moments of uncertainty, in which he has always been able to address me at best, making me look at the glass as half-full. It is a quality not to be taken for granted.

I would like to acknowledge my internal supervisor and co-supervisor, Professors Viola Schiaffonati and Letizia Tanca, always very kind and helpful, who have been able to effectively support me remotely in a notoriously not easy time, providing me with essential advice and feedback.

I would also like to thank my external co-supervisor, Professor Karine Gentelet, who unfortunately I never had the opportunity to meet in person for reasons of force majeure, but whose precious contribution has enriched this research work, allowing it to get out of the ordinary and to include interesting and diversified perspectives.

In addition, I would like to acknowledge my friends for having brightened my days, being close to me in difficult times, and having shared with me many meaningful experiences of my life and several unforgettable moments.

Finally, I would like to thank my parents and my grandparents, Angelo and Palma, who have always supported me throughout these difficult years, not only economically but also emotionally, pushing me not to give up and pursue new life experiences that may have enriched me, even knowing that those experiences, in some cases, would have taken me far from them.
